A Wait-Free Queue with\\ Polylogarithmic Step Complexity

### 2023-06-21 presentation/podc-presentation.tex
added photo
minor edits

\title{A Wait-Free Queue with Polylogarithmic Step Complexity}

@@

\begin{frame}
\maketitle
\end{frame}

@@

Problem:  implement lock-free FIFO queue
\begin{itemize}
\item shared by $p$ processes
\item use single-word CAS (reasonable-sized words)
\item support multiple enqueuers, dequeuers
\end{itemize}

@@

\medskip
\visible<4->{
\begin{itemize}
\item one CAS of next pointer succeeds.
\item other \op{Enqueues} must try again.
\item<5> $\Rightarrow$ starvation and $\Omega(p)$ steps per operation (amortized)
\end{itemize}
}
\end{frame}

@@

Other \Red{list-based} queues
\begin{itemize}
\item
add elimination array \hfill {\small [Moir et al.\ 2005]}
\item
baskets queue \hfill {\small [Hoffman, Shalev, Shavit 2007]}
\item
doubly-linked list + optimism \hfill {\small [Ladan-Mozes, Shavit 2008]}
\item
fast path, slow path \hfill {\small [Kogan, Petrank 2012]}
\item
futures \hfill {\small [Kogan, Herlihy 2014]}
\end{itemize}
\visible<2->{All have CAS retry problem  \hfill {\small [Morrisson, Afek 2013]}}

@@

Previous lock-free queues take $\Omega(p)$ steps per operation.

>>>>

\title{A Wait-Free Queue with\\
Polylogarithmic Step Complexity}

@@

\begin{frame}
\maketitle
\hspace*{29mm}\includegraphics[width=5cm]{Hossein.jpeg}

@@

Problem:  implement linearizable, lock-free FIFO queue
\begin{itemize}
\item shared by $p$ processes
\item use single-word CAS (reasonable-sized words)
\item support multiple enqueuers, dequeuers
\end{itemize}

@@

\medskip
\visible<3->{
\begin{itemize}
\item<3-> one CAS of next pointer succeeds.
\item<4-> other \op{Enqueues} must try again.
\item<5> $\Rightarrow$ starvation and $\Omega(p)$ steps per operation (amortized)
\end{itemize}
}
\end{frame}

@@

Other \Red{list-based} queues
\begin{itemize}
\item
add elimination array \hfill {\small [Moir et al.\ 2005]}
\item
baskets queue \hfill {\small [Hoffman, Shalev, Shavit 2007]}
\item
doubly-linked list + optimism \hfill {\small [Ladan-Mozes, Shavit 2008]}
\item
fast path, slow path \hfill {\small [Kogan, Petrank 2012]}
\item
futures \hfill {\small [Kogan, Herlihy 2014]}
\end{itemize}
\visible<2->{All have CAS retry problem  \hfill {\small [Morrison, Afek 2013]}}

@@

%\medskip
%
%Previous lock-free queues take $\Omega(p)$ steps per operation.
